### 2024-06-19 out/10._Notations_and_conventions/05._Parts_of_hallway.tex
make inner walls lines

Let \(a\) and \(c\) be the lines \(x=1\) and \(y=1\) representing the \emph{outer walls} of \(L\) passing through \(\mathbf{y}\). Let \(b\) and \(d\) be the half-lines \((-\infty, 0] \times \left\{ 0 \right\}\) and \(\left\{ 0 \right\} \times (-\infty, 0]\) representing the \emph{inner walls} of \(L\) emanating from the inner corner \(\mathbf{x}\).

>>>>

Let \(a\) and \(c\) be the lines \(x=1\) and \(y=1\) representing the \emph{outer walls} of \(L\) passing through the outer corner \(\mathbf{y}\).
Let \(b\) and \(d\) be the lines \(x=0\) and \(y=0\) representing the \emph{inner walls} of \(L\) passing through the inner corner \(\mathbf{x}\).
